Power to the Stimuli: Not the Effect

### 2022-08-12 manuscript_draft.Rmd
updating with simulations outside the manuscript

```{r sim_pop, include = F, echo = F}
# small potential variability overall, sort of 1-7ish scale
mu1 <- rnorm(30, 4, .25)
sigma1.1 <- rnorm(30, 2, .2)
sigma2.1 <- rnorm(30, 2, .4)
sigma3.1 <- rnorm(30, 2, .8)

# medium potential variability 0 to 100 scale
mu2 <- rnorm(30, 50, 10)
sigma1.2 <- rnorm(30, 25, 4)
sigma2.2 <- rnorm(30, 25, 8)
sigma3.2 <- rnorm(30, 25, 16)

while(sum(sigma3.2 < 0) > 0){
  sigma3.2 <- rnorm(30, 25, 16)
}

# large potential variability in the 1000s scale
mu3 <- rnorm(30, 1000, 150)
sigma1.3 <- rnorm(30, 400, 50)
sigma2.3 <- rnorm(30, 400, 100)
sigma3.3 <- rnorm(30, 400, 200)

while(sum(sigma3.3 < 0) > 0){
  sigma3.3 <- rnorm(30, 400, 200)
}

population1 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma1.1),
            rnorm(1000*30, mean = mu2, sd = sigma1.2),
            rnorm(1000*30, mean = mu3, sd = sigma1.3))
  )

population2 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma2.1),
            rnorm(1000*30, mean = mu2, sd = sigma2.2),
            rnorm(1000*30, mean = mu3, sd = sigma2.3))
  )

population3 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma3.1),
            rnorm(1000*30, mean = mu2, sd = sigma3.2),
            rnorm(1000*30, mean = mu3, sd = sigma3.3))
  )
```

@@

```{r sim_sample, include = F, echo = F}
# create pilot samples from 20 to 100
samples1 <- samples2 <- samples3 <- list() 
sizes <- c(20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100)
for (i in 1:length(sizes)){
  samples1[[i]] <- population1 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])

  samples2[[i]] <- population2 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])

  samples3[[i]] <- population3 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])
}
```

@@

```{r calc_SE, include = F, echo = F}
# calculate the SEs and the cutoff scores 
SES1 <- SES2 <- SES3 <- list()
cutoffs1 <- cutoffs2 <- cutoffs3 <- list()
sd_items1 <- sd_items2 <- sd_items3 <- list()
for (i in 1:length(samples1)){
  sd_items1[[i]] <- samples1[[i]] %>% group_by(item, scale) %>% 
    summarize(sd = sd(score), .groups = "keep") %>% 
    ungroup() %>% group_by(scale) %>% summarize(sd_item = sd(sd))
  sd_items2[[i]] <- samples2[[i]] %>% group_by(item, scale) %>% 
    summarize(sd = sd(score), .groups = "keep") %>% 
    ungroup() %>% group_by(scale) %>% summarize(sd_item = sd(sd))
  sd_items3[[i]] <- samples3[[i]] %>% group_by(item, scale) %>% 
    summarize(sd = sd(score), .groups = "keep") %>% 
    ungroup() %>% group_by(scale) %>% summarize(sd_item = sd(sd))

  SES1[[i]] <- tapply(samples1[[i]]$score,
                     list(samples1[[i]]$item,
                          samples1[[i]]$scale),
                     function (x){ sd(x)/sqrt(length(x))})
  SES2[[i]] <- tapply(samples2[[i]]$score,
                   list(samples2[[i]]$item,
                        samples2[[i]]$scale),
                   function (x){ sd(x)/sqrt(length(x))})
  SES3[[i]] <- tapply(samples3[[i]]$score,
                 list(samples2[[i]]$item,
                      samples2[[i]]$scale),
                 function (x){ sd(x)/sqrt(length(x))})

  cutoffs1[[i]] <- apply(as.data.frame(SES1[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
  cutoffs2[[i]] <- apply(as.data.frame(SES2[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
  cutoffs3[[i]] <- apply(as.data.frame(SES3[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
}
```

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 500 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams or have participant funds. The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

```{r sim_sim, include = F, echo = F}
# sequence of sample sizes to try
samplesize_values <- seq(20, 500, 5)

# place to store everything
sampled_values1 <- sampled_values2 <- sampled_values3 <- list()

# loop over the samples
for (i in 1:length(samples1)){

  # create a blank table for us to save the values in 
  sim_table1 <- matrix(NA, 
                      nrow = length(samplesize_values), 
                      ncol = 30*3)

  # make it a data frame
  sim_table1 <- sim_table2 <- sim_table3 <- as.data.frame(sim_table1)

  # add a place for sample size values 
  sim_table1$sample_size <- sim_table2$sample_size <- sim_table3$sample_size <- NA

  # loop over pilot sample sizes
  for (q in 1:length(samplesize_values)){

    # temp dataframe that samples and summarizes
    temp <- samples1[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table1[q, 1:90] <- temp$se
    sim_table1[q, 91] <- samplesize_values[q]

    temp <- samples2[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table2[q, 1:90] <- temp$se
    sim_table2[q, 91] <- samplesize_values[q]

    temp <- samples3[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table3[q, 1:90] <- temp$se
    sim_table3[q, 91] <- samplesize_values[q]

    } # end pilot sample loop

  sampled_values1[[i]] <- sim_table1
  sampled_values2[[i]] <- sim_table2
  sampled_values3[[i]] <- sim_table3

} # end all sample loop 
```

@@

```{r calc_percent, include = F, echo = F}
summary_list1 <- summary_list2 <- summary_list3 <- list()
for (i in 1:length(sampled_values1)){

  # summary list 1 ----
  summary_list1[[i]] <- sampled_values1[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 1
  temp1.1 <- summary_list1[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "low")

  temp1.2 <- summary_list1[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "low")

  temp1.3 <- summary_list1[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "low")

  #rejoin 
  summary_list1[[i]] <- bind_rows(temp1.1, temp1.2, temp1.3)

  # summary list 2 ----
  summary_list2[[i]] <- sampled_values2[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 2
  temp2.1 <- summary_list2[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "med")

  temp2.2 <- summary_list2[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "med")

  temp2.3 <- summary_list2[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "med")

  #rejoin 
  summary_list2[[i]] <- bind_rows(temp2.1, temp2.2, temp2.3)

  # summary list 3 ----
  summary_list3[[i]] <- sampled_values3[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 3 
  temp3.1 <- summary_list3[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  temp3.2 <- summary_list3[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  temp3.3 <- summary_list3[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  #rejoin 
  summary_list3[[i]] <- bind_rows(temp3.1, temp3.2, temp3.3)

  }

summary_DF <- bind_rows(summary_list1, 
                        summary_list2, 
                        summary_list3)
```

```{r calc_percent_combine, include = F, echo = F}
summary_long_80 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .80) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 80)

summary_long_85 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .85) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 85)

summary_long_90 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .90) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 90)

summary_long_95 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .95) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 95)

summary_long <- rbind(summary_long_80, 
                      summary_long_85,
                      summary_long_90,
                      summary_long_95)

summary_long$source <- factor(summary_long$source, 
                              levels = c("low", "med", "high"),
                              labels = c("Low Variance", "Medium Variance", "High Variance"))

summary_long$scale2 <- factor(summary_long$scale, 
                              levels = c(1:3),
                              labels = c("Small Scale", "Medium Scale", "Large Scale"))

sd_items <- bind_rows(sd_items1, sd_items2, sd_items3)
sd_items$original_n <- rep(rep(sizes, each = 3), 3)
sd_items$source <- rep(c("Low Variance", "Medium Variance", "High Variance"), each = 3*length(sizes))
summary_long <- summary_long %>% 
  full_join(sd_items, 
            by = c("original_n" = "original_n", "scale" = "scale", 
                   "source" = "source"))

summary_long$name <- gsub("Percent_Below", "Decile ", summary_long$name)
```

@@

@@

```{r R2_cutoff, include = F, echo = F}
by_cutoff <- list()
R2 <- list()

@@

```{r import_data, include = F, echo = F}
conDF <- import("./data/concreteness_trial.rda")
elpDF <- import("./data/ELPDecisionData.zip")
```

@@

```{r con_estimate, echo = F, include = F}
# sample the data
con_words <- sample(unique(conDF$Word), size = 100, replace = F)
con_small <- conDF %>% filter(Word %in% con_words)
con_small$Word <- droplevels(con_small$Word)
pilot_size <- round(mean(tapply(con_small$Rating, con_small$Word, length)))

@@

```{r con_sample, include = F, echo = F}
# sequence of sample sizes to try
samplesize_values <- seq(20, 300, 5)

@@

```{r elp_estimate, echo = F, include = F}
# sample the data
elp_fake <- sample(unique(elpDF$Stimulus[elpDF$Type == 0]), size = 500, replace = F)
elp_real <- sample(unique(elpDF$Stimulus[elpDF$Type == 1]), size = 500, replace = F)
elp_small <- elpDF %>% filter(Stimulus %in% c(elp_fake, elp_real))
pilot_size <- round(mean(tapply(elp_small$RT, elp_small$Stimulus, length)))

@@

```{r elp_sample, include = F, echo = F}
# sequence of sample sizes to try
samplesize_values <- seq(20, 300, 5)

>>>>

@@

@@

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 2000 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams or have participant funds; however, the sample size simulations were estimated over this amount to determine the pattern of suggested sample sizes (i.e., the function between original sample size and proposed sample size). The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

@@

In this procedure, we identified three points of simulation: the population, the samples from those populations, and the researcher sample simulation. In order to minimize any potentially random quirks, we ran each of these samples 100 times for a total of 1000000 simulations. The average of these simulations is presented in the results.

@@

```{r import-data}

@@

```{r R2-cutoff, include = F, echo = F}
by_cutoff <- list()
R2 <- list()

@@

```{r import-data-example, include = F, echo = F}
conDF <- import("./data/concreteness_trial.rda")
elpDF <- import("./data/ELPDecisionData.zip")
```

@@

```{r con-estimate, echo = F, include = F}
# sample the data
con_words <- sample(unique(conDF$Word), size = 100, replace = F)
con_small <- conDF %>% filter(Word %in% con_words)
con_small$Word <- droplevels(con_small$Word)
pilot_size <- round(mean(tapply(con_small$Rating, con_small$Word, length)))

@@

```{r con-sample, include = F, echo = F}
# sequence of sample sizes to try
samplesize_values <- seq(20, 300, 5)

@@

```{r elp-estimate, echo = F, include = F}
# sample the data
elp_fake <- sample(unique(elpDF$Stimulus[elpDF$Type == 0]), size = 500, replace = F)
elp_real <- sample(unique(elpDF$Stimulus[elpDF$Type == 1]), size = 500, replace = F)
elp_small <- elpDF %>% filter(Stimulus %in% c(elp_fake, elp_real))
pilot_size <- round(mean(tapply(elp_small$RT, elp_small$Stimulus, length)))

@@

```{r elp-sample, include = F, echo = F}
# sequence of sample sizes to try
samplesize_values <- seq(20, 300, 5)
